---
title: "anonymous-bootwar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{anonymous-bootwar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This vignette shows how to play bootwar using a deck built with an anonymous function rather than the standard 52 card deck.

### Initialization:

```{r}
# Load bootwar
library(bootwar)

# Set up vectors for computer and player's cards and values
comp_cv <- vector(mode = "character")
comp_vv <- vector(mode = "numeric")
plyr_cv <- vector(mode = "character")
plyr_vv <- vector(mode = "numeric")
```


### Define Custom Deck

Use the deck_of_cards parameter of shuffle_deck() to define a custom deck of cards.

```{r}
seed <- 123
set.seed(seed)

# Shuffle the deck
ideck <- shuffle_deck(
  deck_of_cards = function(x) {as.integer(stats::runif(52, 1, 208))},
  seed = seed
  )

head(ideck)
```


The rest of the workflow follows the same structure as the README.

### Play the First Round:

```{r}
rres <- play_round(cdeck = ideck,
                   plyr_cv = plyr_cv, plyr_vv = plyr_vv,
                   comp_cv = comp_cv, comp_vv = comp_vv)
```


### Continue the Game for Four More Rounds:

```{r}
for (i in 1:4) {
  rres <- play_round(cdeck = rres$updated_deck,
                     plyr_cv = rres$plyr_cv, plyr_vv = rres$plyr_vv,
                     comp_cv = rres$comp_cv, comp_vv = rres$comp_vv)
}

# Ensure 10 cards have been dealt
nrow(rres$updated_deck)
```


### Analyze the Game:

```{r}
gres <- analyze_game(plyr_vv = rres$plyr_vv, comp_vv = rres$comp_vv,
                     mode = "pt", nboot = 1000, seed = 150, conf.level = 0.05)

# Display game results
gres$winner
gres$bootstrap_results$effect.size
gres$bootstrap_results$ci.effect.size
gres$bootstrap_results$p.value
```
